### 2015-04-20 paper.tex
Add turbine description

\section*{Materials and Methods}
\subsection*{Etiam eget sapien nibh.}

% For figure citations, please use "Fig." instead of "Figure".
Nulla mi mi, Fig.~\ref{fig1} venenatis sed ipsum varius, volutpat euismod diam.
Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim rutrum.
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo vitae
nulla elementum commodo eu id massa. In vitae diam ac augue semper tincidunt eu
ut eros. Fusce fringilla erat porttitor lectus cursus, \nameref{S1_Video} vel
sagittis arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque.
Praesent faucibus semper libero.

\begin{figure}[h]
\caption{{\bf Figure Title first bold sentence Nulla mi mi, venenatis sed ipsum 
varius, volutpat euismod diam.}
Figure Caption Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim 
rutrum. A: Lorem ipsum dolor sit amet. B: Consectetur adipiscing elit.}
\label{fig1}
\end{figure}

\begin{enumerate}
\item{react}
\item{diffuse free particles}
\item{increment time by dt and go to 1}
\end{enumerate}

% Results and Discussion can be combined.
\section*{Results and Discussion}
Nulla mi mi, venenatis sed ipsum varius, Table~\ref{table1} volutpat euismod
diam. Proin rutrum vel massa non gravida. Quisque tempor sem et dignissim
rutrum. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Morbi at justo
vitae nulla elementum commodo eu id massa. In vitae diam ac augue semper
tincidunt eu ut eros. Fusce fringilla erat porttitor lectus cursus, vel sagittis
arcu lobortis. Aliquam in enim semper, aliquam massa id, cursus neque. Praesent
faucibus semper libero.

>>>>

\section*{Materials and Methods}
\subsection*{Turbine Model}

% For figure citations, please use "Fig." instead of "Figure".
A 1:6 scale model of the RM2 rotor was designed and built. Turbine geometric
parameters were scaled from the RM2 ``rev 0'' design report \cite{Barone2011},
with the exception of the shaft diameter, which was scaled from the SAFL RM2
shaft \cite{Hill2014}. The hubs were designed to be similar to the SAFL model,
which may aid in comparison of the results, though this was not a top priority.
Geometric parameters are shown in Table~\ref{tab:turb-geom} and a drawing of the
turbine design is shown in Figure~\ref{fig:turbine-drawing}. The turbine model
components---blades, struts, shaft, and center hub sections---were fabricated
from 6061-T6 aluminum, which was hardcoat anodized per MIL-8625-A, type III,
class 2 specifications. CAD models of the turbine are available from
\cite{Bachant2015-RM2-CAD}.

\begin{table}[ht]
\centering
\begin{tabular}{l|l|l}
   & Full-scale & Model (1:6) \\
\hline 
Diameter (m)   & 6.450 & 1.075 \\ 
Height (m)     & 4.840 & 0.8067 \\ 
Blade root chord (m) & 0.4000 & 0.06667 \\ 
Blade tip chord (m)  & 0.2400 & 0.04000 \\ 
Blade profile & NACA 0021 & NACA 0021 \\ 
Blade mount & 1/2 chord & 1/2 chord \\ 
Blade pitch (deg.) & 0.0 & 0.0 \\ 
Strut profile & NACA 0021 & NACA 0021 \\ 
Strut chord (m) & 0.3600 & 0.06000 \\ 
Shaft diameter (m) & 0.2540 \cite{Beam2011} or 0.4160 \cite{Hill2014} & 0.06350\\ 
\end{tabular}
\caption{RM2 turbine geometric parameters.}
\label{tab:turb-geom}
\end{table}

\begin{figure}[h]
\caption{{\bf Turbine Model Drawing.}
Drawing of the turbine with and without strut covers.}
\label{fig:turbine-drawing}
\end{figure}

\section*{Results and Discussion}
